---
title: "Data Cleaning Report S23"
author: "Kennedy Zapalac"
date: "2023-05-24"
output: pdf_document
---

```{r requires user input, include=FALSE}
# change these depending on what dataset you are cleaning

# file names -------------------------------------------------------------------
# the files are pulled from whatever directory this document is in, so include any subfolders from your current directory
# if the files aren't directly in this directory
raw_completed_pre_filename <-  "S23Pre-test_completed_041223 copy.csv" # don't forget to include .csv at the end of the file name
raw_inProgress_pre_filename <-  NULL # optional if you are analyzing the data before all responses have been deemed complete
raw_completed_post_filename <-  "S23Post-test_completed_042123 copy.csv"
raw_inProgress_post_filename <-  "S23Post-test_inProgress_042123 copy.csv" # optional if you are analyzing the data before all responses have been deemed complete
cleaned_pre_filename <-  "S23Pre-test_cleaned.csv"
cleaned_post_filename <-  "S23Post-test_cleaned.csv"
matched_pre_and_post_filename <- "S23matched_data_cleaned.csv"

# Composite Variables ----------------------------------------------------------
# if you want to compute anything other than averages, you will need to edit the code below in pretest and postest data processing
# list of variables you would like to create a composite for, using the question abbreviations from the survey:
comp_vars <- c("ERQ", "StressM", "MWQ", "RS", "GrowM", "SelfEf", "Motiv")
# list of the number of questions for each composite above
comp_vars_n_qs <- c(6, 4, 5, 6, 3, 3, 3)

# Important Notes --------------------------------------------------------------
# You may still need to edit the code slightly below to work for your specific dataset
# There are a few sections highlighted with "CHECK THIS" that you should take a look at

# Errors you may encounter:
  # improper column names
  # data that doesn't exist but has code referring to it (one survey may test resilience while another does not)
  # Some of the code was altered. For example, if you edit a variable name somewhere
    # and later code references the old variable name, then it will no longer be able to find
    # that variable

# To overcome these potential errors:
  # 1. Make sure to use proper column names when creating the survey (listed in Research Partnerships manual)
    # and change any improper column names before running this script
  # 2. Comment out code for the variables that don't exist in your dataset
    # E.g., composites created for non-existent variables in this dataset

# Even if you are able to run this code without errors, you should check to make sure
# it is working properly. Check the data cleaning report by knitting this document 
# after altering the script for your dataset (if necessary). Make sure that nothing seems awry here.
# For example, it would be fishy if no previews are removed if you know there are
# previews within the dataset.
# Also, read over the whole script and make sure that you know what it's doing
# This will prevent any hidden errors that might not be apparent in the data report
```

```{r setup, include=FALSE}
# install (if needed) and load packages 
# install.packages("tidyverse")
library(tidyverse)
# install.packages("ggplot2")
library(ggplot2)
# install.pacakges("psych")
library(psych)

# homemade functions
source("data_cleaning_functions.R") # file must be in the working directory
```

```{r pretest data processing, include=FALSE}
# load and clean the data
pre_data <- load_data(completed_file = raw_completed_pre_filename, inProgress_file = raw_inProgress_pre_filename )

# CHECK THIS: variables names ------------------------------------------------------------------
# and change this section according to your needs #
# rename improper columns (ideally there shouldn't be any if you use the format recommended in the manual when creating the survey in Qualtrics)
pre_data <- rename_cols(data=pre_data, oldSubString = "StressM_", newSubString = "StressM")
colnames(pre_data)[which(names(pre_data)=='1_student_ID')] <- "student_ID"
colnames(pre_data)[which(names(pre_data)=='1_student_ID2')] <- "student_ID2"
pre_data <- pre_data %>%
  rename('birthday_1' = 'Birthday_pre_1',
         'birthday_2' = 'Birthday_pre_2',
         'birthday_3' = 'Birthday_pre_3')
  
# finish reformatting the columns ----------------------------------------------
 # if there are any other columns
  # that will need to be removed repeatedly in the future, please add them to the function
pre_data <- create_teacher_col(data=pre_data)
pre_data$teacher <- sub("=", "", pre_data$teacher)
pre_data <- reformat_bday(data=pre_data) # won't need this in the future if we provide answer choices
pre_data <- convert_dtypes(data=pre_data)

# remove responses -------------------------------------------------------------
pre_length_raw <- nrow(pre_data) # record the unprocessed number of responses
pre_data <- remove_previews(pre_data) # record the number of previews removed
pre_previews <- pre_length_raw - nrow(pre_data)
pre_data <- remove_blank(data=pre_data)
pre_blanks <- pre_length_raw - pre_previews - nrow(pre_data) # record the number of blank responses removed
duplicates_keep <- select_duplicates(pre_data, pre=T)
pre_data <- remove_duplicates(pre_data)
pre_data <- rbind(pre_data, duplicates_keep) # add the duplicates we are keeping back
pre_duplicates <- pre_length_raw - pre_previews - pre_blanks - nrow(pre_data) # record the number of duplicates removed
# double check that there are no duplicates remaining
n_student_ID <- data.frame(table(pre_data$student_ID))
pre_data_duplicates_cleaned <- pre_data[pre_data$student_ID %in% n_student_ID$Var1[n_student_ID$Freq > 1],]
pre_data_n_duplicates_cleaned <- sum(duplicated(pre_data$student_ID))
# check how many responses were removed during cleaning
pre_total_removed <- pre_previews + pre_blanks + pre_duplicates
pre_removed_responses <- data.frame(previews=pre_previews, blank=pre_blanks, duplicates=pre_duplicates, total=pre_total_removed)
# num of students after cleaning
pre_cleaned_total_responses <- nrow(pre_data)

# create composites ------------------------------------------------------------
# this function computes averages, which might not be appropriate depending on your dataset
pre_data <- create_composites(data=pre_data, Q_names=comp_vars, Q_numbers=comp_vars_n_qs, pre=T)

# room for growth (ideal focus > actual focus)
pre_data$room_to_grow <- pre_data$undivided_ideal_pre_1 > pre_data$undivided_actual_pre_1

# attention check --------------------------------------------------------------
# passed attention check
pre_passed_att_check <- sum(pre_data$ATT_CHECK_pre, na.rm=T)
pre_percent_passed_att_check <- (round(pre_passed_att_check/pre_cleaned_total_responses, digits=3))*100
pre_failed_att_check <- sum(pre_data$ATT_CHECK_pre==0, na.rm=T)
pre_percent_failed_att_check <- (round(pre_failed_att_check/pre_cleaned_total_responses, digits=3))*100
pre_att_check_missing <- sum(is.na(pre_data$ATT_CHECK_pre))
pre_percent_att_check_missing <- (round(pre_att_check_missing/pre_cleaned_total_responses, digits=3))*100

# save the cleaned data --------------------------------------------------------
write.csv(pre_data, cleaned_pre_filename, row.names=F)
```

```{r postest data processing, include=FALSE}
# load and clean the data
post_data <- load_data(completed_file = raw_completed_post_filename, inProgress_file = raw_inProgress_post_filename)

# CHECK THIS: variable names ------------------------------------------------------------------
# change this section according to your needs ##
# rename improper columns (ideally there shouldn't be any if you use the format recommended in the manual when creating the survey in Qualtrics)
# # there aren't any for this dataset since I created this template based on this dataset
post_data <- rename_cols(data=post_data, oldSubString = "StressM_", "StressM")
colnames(post_data)[which(names(post_data)=='1_student_ID')] <- "student_ID"
colnames(post_data)[which(names(post_data)=='1_student_ID2')] <- "student_ID2"
post_data <- post_data %>% 
  rename('birthday_1' = 'Birthday_post_1', 
         'birthday_2' = 'Birthday_post_2',    
         'birthday_3' = 'Birthday_post_3')

# finish reformatting the columns ----------------------------------------------
post_data <- remove_col_spaces(data=post_data)
post_data <- remove_extra_cols(data=post_data) # if there are any other columns
  # that will need to be removed repeatedly in the future, please add them to the function
post_data <- create_teacher_col(data=post_data)
post_data$teacher <- sub("=", "", post_data$teacher)
post_data <- reformat_bday(data=post_data) # won't need this in the future if we provide answer choices
post_data <- convert_dtypes(data=post_data)

# remove responses -------------------------------------------------------------
post_length_raw <- nrow(post_data) # record the unprocessed number of responses
post_data <- remove_previews(post_data) # record the number of previews removed
post_previews <- post_length_raw - nrow(post_data)
post_data <- remove_blank(data=post_data)
post_blanks <- post_length_raw - post_previews - nrow(post_data) # record the number of blank responses removed
duplicates_keep <- select_duplicates(post_data, pre=F)
post_data <- remove_duplicates(post_data)
post_data <- rbind(post_data, duplicates_keep) # add the duplicates we are keeping back
post_duplicates <- post_length_raw - post_previews - post_blanks - nrow(post_data) # record the number of duplicates removed
# double check that there are no duplicates remaining
n_student_ID <- data.frame(table(post_data$student_ID))
post_data_duplicates_cleaned <- post_data[post_data$student_ID %in% n_student_ID$Var1[n_student_ID$Freq > 1],]
post_data_n_duplicates_cleaned <- sum(duplicated(post_data$student_ID))
# check how many responses were removed during cleaning
post_total_removed <- post_previews + post_blanks + post_duplicates
post_removed_responses <- data.frame(previews=post_previews, blank=post_blanks, duplicates=post_duplicates, total=post_total_removed)
# num of students after cleaning
post_cleaned_total_responses <- nrow(post_data)

# create composites ------------------------------------------------------------
# this function computes averages, which might not be appropriate depending on your dataset
post_data <- create_composites(data=post_data, Q_names=comp_vars, Q_numbers=comp_vars_n_qs, pre=F)
# had to create this composite by hand since it's only present in the post df
# could have included it in the list for Q_names above just for the post df
post_data$CQ_score <- post_data %>% 
  select('CQ1_post', 'CQ2_post', 'CQ3_post') %>% 
  rowSums(na.rm=T)/3

# attention check --------------------------------------------------------------
# passed attention check
post_passed_att_check <- sum(post_data$ATT_CHECK_post, na.rm=T)
post_percent_passed_att_check <- (round(post_passed_att_check/post_cleaned_total_responses, digits=3))*100
post_failed_att_check <- sum(post_data$ATT_CHECK_post==0, na.rm=T)
post_percent_failed_att_check <- (round(post_failed_att_check/post_cleaned_total_responses, digits=3))*100
post_att_check_missing <- sum(is.na(post_data$ATT_CHECK_post))
post_percent_att_check_missing <- (round(post_att_check_missing/post_cleaned_total_responses, digits=3))*100

# save the cleaned data --------------------------------------------------------
write.csv(post_data, cleaned_post_filename, row.names=F)
```

```{r combine data, include=FALSE}
# sort by the student IDs
pre_data <- pre_data %>% arrange(student_ID)
post_data <- post_data %>% arrange(student_ID)

# CHECK THIS: birthdays included? -------------------------------------------------------------------
# You might be able to match with ID and teacher or with birthday and teacher
# Comment or uncomment the appropriate code depending on what is present in your dataset

# match pre and post data (can do this under the hood with combine_pre_post function, but wanted to get numbers)
matched_IDs <- match_IDs(pre_data=pre_data, post_data=post_data)
n_ID_matches <- nrow(matched_IDs) # record the number of students with matched IDs
matched_birthday_teacher <- match_birthday_teacher(pre_data=pre_data, post_data=post_data)
n_birthday_teacher_matches <- nrow(matched_birthday_teacher) # record the number of students with matched bdays

# match pre and post data (function)
matched_pre_and_post_data <- combine_pre_post(pre_data=pre_data, post_data=post_data)


# save the cleaned and matched data to a new file
write.csv(matched_pre_and_post_data, matched_pre_and_post_filename, row.names=F)
```

# Check that the data was cleaned properly by reading the report below

## Pre-Course Survey Data Processing
Raw data source (there should be 2 if you pulled the "Recorded" and "In Progress" responses from Qualtrics):

-   `r raw_completed_pre_filename`
-   `r raw_inProgress_pre_filename`

These are the variables you computed composites for:

-   `r comp_vars`

These are the corresponding numbers of questions for the variables you computed composites for:

-   `r comp_vars_n_qs`

Here is a list of all the variables contained in the dataset: 

-   `r colnames(pre_data)`

There was originally r pre_length_raw` rows of data from the pre-course survey. We removed `r pre_previews` previews from our team members, `r pre_blanks` blank responses, and `r pre_duplicates` duplicates. In total, we removed `r pre_total_removed` rows from the pre-course survey data. This left us with `r pre_cleaned_total_responses` pre-course survey responses.

Of the `r pre_cleaned_total_responses` total respondents, `r pre_passed_att_check` (`r pre_percent_passed_att_check`%) passed the attention check, whereas `r pre_failed_att_check` (`r pre_percent_failed_att_check`%) failed the attention check, and `r pre_att_check_missing` (`r pre_percent_att_check_missing`%) did not answer the attention check question.

Here is how many respondents there were by teacher:
```{r pre teachers, echo=FALSE}
table(pre_data$teacher)
```

You saved the cleaned dataset as: `r cleaned_pre_filename`

## Post-Course Survey Data Processing

Raw data source (there should be 2 if you pulled the "Recorded" and "In Progress" responses from Qualtrics):

-   `r raw_completed_post_filename`
-   `r raw_inProgress_post_filename`

These are the variables you computed composites for:

-   `r comp_vars`

These are the corresponding numbers of questions for the variables you computed composites for:

-   `r comp_vars_n_qs`

Here is a list of all the variables contained in the dataset: 

-   `r colnames(post_data)`

There was originally `r post_length_raw` rows of data from the post-course survey. We removed `r post_previews` previews from our team members, `r post_blanks` blank responses, and `r post_duplicates` duplicates. In total, we removed `r post_total_removed` rows from the post-course survey data. This left us with `r post_cleaned_total_responses` post-course survey responses.

Of the `r post_cleaned_total_responses` total respondents, `r post_passed_att_check` (`r post_percent_passed_att_check`%) passed the attention check, whereas `r post_failed_att_check` (`r post_percent_failed_att_check`%) failed the attention check, and `r post_att_check_missing` (`r post_percent_att_check_missing`%) did not answer the attention check question.

Here is how many respondents there were by teacher:
```{r post teachers, echo=FALSE}
table(post_data$teacher)
```

You saved the cleaned dataset as: `r cleaned_post_filename`

## Combing Pre and Post Data
The pre-course survey had `r nrow(pre_data)` respondents, and the post-course survey had `r nrow(post_data)` respondents. If we were able to match all of our pre and post surveys, we would have had `r min(c(nrow(pre_data), nrow(post_data)))` matches. However, we had `r nrow(matched_pre_and_post_data)` matched pre and post-course surveys. We were able to match `r n_ID_matches` by their student ID and teacher, and we matched `r n_birthday_teacher_matches` more students based on their birthday and teacher.

Here is a list of all the variables contained in the dataset:

-   `r colnames(matched_pre_and_post_data)`

Here is how many respondents there were by teacher:
```{r pre and post teachers, echo=FALSE}
table(matched_pre_and_post_data$teacher)
```

You saved the matched pre and post dataset as: `r matched_pre_and_post_filename`

